---
title: "RFLOMICS-install"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RFLOMICS-install}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(RFLOMICS)
```

# What is clutstermq
[clustermq](https://github.com/mschubert/clustermq) is a R package which allow to send functions calls as jobs on a computing cluster with a minimal interface provided by the Q function. 
This package is used in RFLOMICS to speed up differential expression and co-expression analysis. 

# clustermq configuration

- Create bioinfo [account](http://bioinfo.genotoul.fr/index.php/ask-for/create-an-account-2/)
- Clustermq is installed on R 4.1.1 version. Thus egdeR and Coseq packages.

## Set up SSH keys for password-less login on Genotoul

  1)  Generate a ssh key in local
  
```{bash, eval=FALSE}

ssh-keygen -t rsa

<!-- Enter file in which to save the key (/home/dcharif/.ssh/id_rsa): -->

```

=> Enter without changing the default location

Enter passphrase (empty for no passphrase):

=> Enter 2 times and let empty

2 keys have been created: on public and one private. The first one has to be send to genotoul
and the second one has to be keeped in your local machine.

  2) Copy the public key to genotoul
This command will put your public key to the authorized_keys file on genotoul.

$ ssh-copy-id dcharif@genologin.toulouse.inra.fr
The authenticity of host 'Server's IP address' can't be established. RSA key fingerprint is ... Are you sure you want to continue connecting (yes/no)?

=> enter yes
=> enter your password

  3) Try to connect know and verify that your password is no more asked

$ ssh dcharif@genologin.toulouse.inra.fr


https://www.hostinger.fr/tutoriels/generer-cle-ssh/

## On own computer 



## On cluster (genotoul server : SLURM)






II) Configure clustermq


     1) Create a file SSH.tmpl in your home directory on your LOCAL machine:

```{bash, eval=FALSE}
ssh -o "ExitOnForwardFailure yes" -f \
    -R {{ ctl_port }}:localhost:{{ local_port }} \
    -R {{ job_port }}:localhost:{{ fwd_port }} \
    {{ ssh_host }} \
    "source /etc/profile\
     module load {{ bashenv }}\
     R --no-save --no-restore -e \
     'clustermq:::ssh_proxy(ctl={{ ctl_port }}, job={{ job_port }})' \
     > {{ ssh_log | /dev/null }} 2>&1"
```     


     2) In your $HOME/.Rprofile on your LOCAL machine:

```{bash, eval=FALSE}
    options(
    clustermq.scheduler = "ssh",
    clustermq.template = "/Users/dcharif/SSH.tmpl",
    clustermq.ssh.host = "dcharif@genologin.toulouse.inra.fr", # use your user and host, obviously
    clustermq.ssh.log = "/home/dcharif/cmq_ssh.log" # log for easier debugging
)
```

    3) In your $HOME/.Rprofile on GENOTOUL set the following options:

```{bash, eval=FALSE}
options(
    clustermq.scheduler = "slurm",
    clustermq.template = "/home/dcharif/clustermq.template",
    clustermq.defaults = list(bashenv="system/R-3.6.0")
)
```  

#ou Q(..., template=list(bashenv="system/R-3.6.0"))

   4) In your $HOME directory on GENOTOUL, create the clustermq.template file

```{bash, eval=FALSE}
#!/bin/sh
#SBATCH --job-name={{ job_name }}
#SBATCH --partition=workq
#SBATCH --output={{ log_file | /dev/null }} # you can add .%a for array index
#SBATCH --error={{ log_file | /dev/null }}
#SBATCH --mem-per-cpu={{ memory | 4096 }}
#SBATCH --array=1-{{ n_jobs }}
#SBATCH --mail-user=delphine.charif@inra.fr

module load {{ bashenv }}

ulimit -v $(( 1024 * {{ memory | 4096 }} ))
CMQ_AUTH={{ auth }} R --no-save --no-restore -e 'clustermq:::worker("{{ master}}")'
```  


