---
title: "RFLOMICS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RFLOMICS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

```


# Run RFLOMICS

```{r, eval=FALSE}
library(RFLOMICS)
runApp()
```

In the left side of interface the different tab Items will be appear as the analysis progresses to guide the user. 

# Load Data

In this section we start to set project name (its mandatory). Then we load the experimental design and different datasets.

<!-- ![capture]() -->

## Load Design

<!-- ![capture]() -->
## Load Omics data 

<!-- ![capture]() -->
# Set statistical model choose contrasts to test


<!-- ![capture]() -->
# Omics data analysis

## QC, Low counts filtering and normalization
<!-- ![capture]() -->
## Differiencial expression analysis
<!-- ![capture]() -->
## Co-Expression analysis
<!-- ![capture]() -->
## Annotation and enrichment analysis
<!-- ![capture]() -->