---
title: "RFLOMICS-install"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RFLOMICS-install}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(RFLOMICS)
```

# What is clustermq ?

[clustermq](https://github.com/mschubert/clustermq) is a R package which allow to send functions calls as jobs on a computing cluster with a minimal interface provided by the Q function. 
This package is used (optionnaly) in RFLOMICS to run differential expression and co-expression analysis on a computing cluster. To turn on this option, you have to configure your environment
as explained below. 

# clustermq configuration

- Create an [account](http://bioinfo.genotoul.fr/index.php/ask-for/create-an-account-2/) on the
genotoul bioinformatic platform.
- Clustermq is installed on R 4.1.1 version. Thus egdeR and Coseq packages.

## Set up SSH keys for password-less login on Genotoul

  1)  Generate a ssh key in local
  
```{bash, eval=FALSE}

ssh-keygen -t rsa

<!-- Enter file in which to save the key (/home/User/.ssh/id_rsa): -->

```

=> Enter without changing the default location

Enter passphrase (empty for no passphrase):

=> Enter 2 times and let empty

2 keys have been created: on public and one private. The first one has to be send to genotoul
and the second one has to be keeped in your local machine.

  2) Copy the public key to genotoul
This command will put your public key to the authorized_keys file on genotoul.

```{bash, eval=FALSE}
ssh-copy-id user@genologin.toulouse.inra.fr
```

The authenticity of host 'Server's IP address' can't be established. RSA key fingerprint is ... Are you sure you want to continue connecting (yes/no)?

=> enter yes

=> enter your password

  3) Try to connect know and verify that your password is no more asked

```{bash, eval=FALSE}
$ ssh user@genologin.toulouse.inra.fr
```

https://www.hostinger.fr/tutoriels/generer-cle-ssh/

## In LOCAL (on your machine)


     1) Create a SSH.tmpl file in your home directory:

```{bash, eval=FALSE}
ssh -o "ExitOnForwardFailure yes" -f \
    -R {{ ctl_port }}:localhost:{{ local_port }} \
    -R {{ job_port }}:localhost:{{ fwd_port }} \
    {{ ssh_host }} \
    "source /etc/profile\
     module load {{ bashenv }}\
     R --no-save --no-restore -e \
     'clustermq:::ssh_proxy(ctl={{ ctl_port }}, job={{ job_port }})' \
     > {{ ssh_log | /dev/null }} 2>&1"
```     


     2) Set the following options in your $HOME/.Rprofile :

```{bash, eval=FALSE}
    options(
    clustermq.scheduler = "ssh",
    clustermq.template = "~/SSH.tmpl",
    clustermq.ssh.host = "user@genologin.toulouse.inra.fr", # use your user and host, obviously
    clustermq.ssh.log = "/home/user/cmq_ssh.log", # log for easier debugging
    clustermq.defaults = list(bashenv="system/R-4.1.1_gcc-9.3.0")
)
```



## On the cluster (Ex: GENOTOUL server with SLURM)

    3) Set the following options in your $HOME/.Rprofile :

```{bash, eval=FALSE}

options(
    clustermq.scheduler = "slurm",
    clustermq.template = "/home/user/clustermq.template",
    clustermq.defaults = list(bashenv="R-4.1.1_gcc-9.3.0")
)

```  


   4) Create the clustermq.template in your $HOME directory 

```{bash, eval=FALSE}
#!/bin/sh
#SBATCH --job-name={{ job_name }}
#SBATCH --partition=workq
#SBATCH --output={{ log_file | /dev/null }} # you can add .%a for array index
#SBATCH --error={{ log_file | /dev/null }}
#SBATCH --mem-per-cpu={{ memory | 4096 }}
#SBATCH --array=1-{{ n_jobs }}
#SBATCH --mail-user=user@inrae.fr

module load {{ bashenv }}

ulimit -v $(( 1024 * {{ memory | 4096 }} ))
CMQ_AUTH={{ auth }} R --no-save --no-restore -e 'clustermq:::worker("{{ master}}")'
```  


