---
title: "RFLOMICS input format"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RFLOMICS-input-data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
)

```

```{r, echo=FALSE}
library(RFLOMICS)
```

RFLOMICS can handle three types of omics (RNAseq, proteomics and metabolomics) and several datasets per omics generated from similar experimental design. Each dataset must have a complete design.

Below each input file is detailed :

## Experimental design file
<!-- ce fichier contient le plan experimental (conditions) plus des metadata par echantillons -->

This file provides the experimental design table. The first column indicates the sample names. Next columns indicate experimental conditions (called biological factors or technical/batch factors) and metadata (optional). Each row describes a sample by specifying the level for each experimental condition.
This file is edited by the user and must contain a header with column names corresponding respectively to the factor names and metadata names.

It is advised that each factor's level starts with a letter (for example, for a factor called Month, it is better to write M1 rather than 1).

```{r ImportDesign, output="asis"}
data(ecoseed)
DT::datatable(ecoseed$design)
```

## Omic data file

For each omics: 
The matrix-like file with abundance of omics data is needed. The first column indicates feature names (genes, proteins, or metabolites), column headers indicate the sample names.

### **Transcriptomics (RNAseq counts data)**

<!-- les comptage de reads sont obtenu après une analyse bioinfo (mapping sur le genome de ref et comptage des reads qui couvrent chaque gene) -->

For RNAseq data the values correspond to raw read counts per genes or transcripts.

```{r RNAseq, output="asis"}
geneCount  <- ecoseed$RNAtest
DT::datatable(geneCount[1:10, 1:5])
```


### **Proteomic data**

For proteomics data the values correspond to intensity of proteins.


```{r Proteomics, output="asis"}
protAbundance <- ecoseed$protetest
DT::datatable(protAbundance[1:10, 1:5])
```


### **Metabolomic data**

For metabolomics data the values correspond to intensity of metabolites.

```{r Metabolomics, output="asis"}
metaAbundance <- ecoseed$metatest
DT::datatable(metaAbundance[1:10, 1:5])
```

## Annotation of features (optional)

This file contains annotation about biological functions of genes/proteins/metabolites, or their implication in biological pathways. This annotation is needed to compute Over Representation Analysis (ORA). This file must contain at least 2 columns, names of features (identical to the ones used in the abundance matrix) and term identifiers (ex. GO term accession : GO:0034599). It is possible to add 2 more columns: names of terms (ex. cellular response to oxidative stress) and the domain of annotation (ex. biological_process).


| Gene ID        | GO term accession | GO term name                              | GO domain          |
|----------------|-------------------|-------------------------------------------|--------------------|
| AT4G36648      | GO:0006412        | translation                               | biological_process |
| AT4G36648      | GO:0030533        | triplet codon-amino acid adaptor activity | molecular_function |
| AT1G18745      | GO:0006396        | RNA processing                            | biological_process |
| AT1G18745      | GO:0005730        | nucleolus                                 | cellular_component |
| AT3G00980      | GO:0006396        | RNA processing                            | biological_process |
| AT3G00980      | GO:0005730        | nucleolus                                 | cellular_component |

