
# `r data` analysis

```{r conditionMeta, echo=FALSE}

dataset.raw.SE <- FlomicsMultiAssay@ExperimentList[[data]]
dataset.SE     <- FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]

Diff.eval <- !is.null(dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]])
CoEx.eval <- !is.null(dataset.SE@metadata[["CoExpAnal"]]$results)

```

## Workflow of reference 

### Dataset processing

```{r CheckDesignMeta, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
check <- CheckExpDesignCompleteness(FlomicsMultiAssay)

NbProt <- length(names(dataset.SE))
NbProtWoutNA <- dim(na.omit(assay(dataset.SE)))[1]
```

* X samples were removed from the datasets.
* The data were `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$transform_method` transformed.
* The number of metabolite: `r NbProt`  
* Number of metabolite with at least 1 NA: `r NbProt - NbProtWoutNA`

### Distribution of density befor/after transformation

```{r densityPlotMeta, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
Data_Distribution_Density.plot(dataset.raw.SE)
Data_Distribution_Density.plot(dataset.SE)
```

### Boxplot and Sum of XIC  

```{r libSize, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
abundanceBoxplot(dataset.SE)
Library_size_barplot.plot(dataset.raw.SE)
```

### Principal component analysis

Multivariate quality check of design. For each design factor (one color for each), and each PCA axis this function plot the coordinates of the sample in a PCA axis (y-axis) in an increasing order along the x-axis. It allows to have a quick view of the percent of variability associated to each factor.

```{r PCAMetabo, echo=FALSE , fig.show="hold", message=FALSE, warning=FALSE,out.width = "100%", eval=TRUE}
mvQCdesign(object = FlomicsMultiAssay,
           data   = paste0(data,".filtred"), PCA="norm", axis=5, 
           pngFile= NULL) 
```

`r if(is.null(dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]])) {"\\begin{comment}"}`

## Differential expression 

Differential abundance of metabolites was carried out thanks to limma package.

 * The lmFit function was used to fit a linear model for each metabolites given the matrix
model constructed during the epxerimental design setup.

 * The selected contrasts were then computed from the fitted model and summary statistics were obtained via the contrasts.fit and eBayes functions (with the robust=T parameter). 

 * P-value of differential expressed metabolites were adjusted according to the `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.method` method
with a cutoff set to `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.cutoff`.


### Results summary


```{r DiffExprMetabo1,echo=FALSE,message=FALSE, out.width = "100%",warning=FALSE,  fig.show = "hold", eval=Diff.eval}

tmpRes <- dataset.SE@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:dim(tmpRes[["contrasts"]])[1]){
   contrastName <- tmpRes[["contrasts"]][i,]$contrastName
   #hyp <- tmpRes[["contrasts"]][i,]$tag
   stats <- tmpRes[["stats"]][[contrastName]]
   DE[i] <- stats$gDE
   DEup[i] <- paste(stats$gDEup," (",stats$pgDEup," %)",sep="")
   DEdown[i] <- paste(stats$gDEdown," (",stats$pgDEdown," %)",sep="")
}
```

```{r DiffExprMetabo2, echo=FALSE, results="asis", eval=Diff.eval}
kable_styling(kable(bind_cols(tmpRes[["contrasts"]][,c("tag","contrastName")], data.frame("Nb DE"=DE,"Nb DEup"=DEup,"Nb DEdown"=DEdown)), row.names=FALSE, caption=NULL, format="html"), font_size=12)
```

The upSet graphic shows the number of DA metabolites (Barplot with Instersection Size) that are specifics to the constrast(s) selected in
the metro card below the barplot. It may help to better view the specificity of the change in metabolite abundance in response to
experimental factors.

```{r DiffExprMetabo3,echo=FALSE, message=FALSE, warning=FALSE,  fig.show = "hold", out.width = "80%", echo=FALSE, eval=Diff.eval}

DEF_mat <- dataset.SE@metadata$DiffExpAnal[["mergeDEF"]]
UpSetR::upset(DEF_mat, sets = (names(DEF_mat[,-1]))) 

```

For each contrasts, 3 graphics are plotted:

 * a distribution of pvalues graph 
 
 * a MA plot: LogFC against average metabolite abundance
 
 * a data.frame given the statistics of limma output by metabolite.


```{r DiffPerContMetabo, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE, eval=Diff.eval}

  out <- NULL
  
  for (contrast  in  dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]]$contrastName) {
    
      out <- c(out, knitr::knit_child("DiffExpAnal_PerContrast.Rmd", quiet=TRUE))  
      
    }
    
knitr::asis_output(out)

```

`r if(is.null(dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]]))  {"\\begin{comment}"}`


`r if(is.null(dataset.SE@metadata[["CoExpAnal"]]$results)) {"\\end{comment}"}`

## Co-expression

Co-expression analysis was carried out on the `r dataset.SE@metadata[["CoExpAnal"]]$merge.type`
of the following list of metabolites `r dataset.SE@metadata$CoExpAnal$gene.list.names`. 
`r dataset.SE@metadata[["CoExpAnal"]]$tools` was
used to cluster them with the following parameters. The gaussian mixture models (`r paste0("model=",dataset.SE@metadata[["CoExpAnal"]]$GaussianModel,"")` was run on scaled by metabolite data to cluster them by expression profile rather than abundance.
`r dataset.SE@metadata[["CoExpAnal"]]$replicates.nb` technical replicates were performed with K=`r dataset.SE@metadata[["CoExpAnal"]]$K.range`. 
The best number of cluster (K) selected via the Integrated Completed Likelihood (ICL) criterion 
was `r dataset.SE@metadata[["CoExpAnal"]]$cluster.nb`.


```{r CoexpMeta, message=FALSE, warning=FALSE, echo=FALSE, message=TRUE, warning=TRUE, eval=CoEx.eval}

  out <- NULL
 
      out <- c(out, knitr::knit_child("CoExpAnal.Rmd", quiet=TRUE))  
    
knitr::asis_output(out)

```

### Data table

```{r CoexpTable, echo=FALSE, results="asis"}
DT::datatable(data.frame(dataset.SE@metadata[["CoExpAnal"]]$coseqResults@allResults[[1]]), 
              options = list(rownames = TRUE, pageLength = 10, scrollX = T, dom = 'tip'),
              class = 'cell-border stripe')
```

`r  if(is.null(dataset.SE@metadata[["CoExpAnal"]]$results)) {"\\end{comment}"}`
