
# `r data` analysis

## Workflow of reference 

## data Exploratory


```{r, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}

plotDistr(abundances= assay(FlomicsMultiAssay[[data]]),
           dataName  = paste0(data,".filtred"), 
          dataType=FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$omicType,
          transform_method=FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$transform_method)

```


`r if(is.null(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]][["contrasts"]])) {"\\begin{comment}"}`

## Differential expression 

Differential expression analysis was carried out for each selected contrast thanks to the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$method` model. 

P-value of differential expressed proteins were adjusted according to the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$Adj.pvalue.method` method
with a cutoff set to `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$Adj.pvalue.cutoff`.

### Results summary

```{r DiffExprProteo1,echo=FALSE,message=FALSE, out.width = "100%",warning=FALSE,  fig.show = "hold"}

tmpRes <- FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:dim(tmpRes[["contrasts"]])[1]){
   contrastName <- tmpRes[["contrasts"]][i,]$contrastName
   #hyp <- tmpRes[["contrasts"]][i,]$tag
   stats <- tmpRes[["stats"]][[contrastName]]
   DE[i] <- stats$gDE
   DEup[i] <- paste(stats$gDEup,"(",stats$pgDEup," %)",sep="")
   DEdown[i] <- paste(stats$gDEdown,"(",stats$pgDEdown," %)",sep="")
}

```

```{r DiffExprProteo2, echo=FALSE, results="asis"}
kable_styling(kable(bind_cols(tmpRes[["contrasts"]][,c("tag","contrastName")], data.frame("Nb DE"=DE,"Nb DEup"=DEup,"Nb DEdown"=DEdown)), row.names=TRUE, caption=NULL, format="html"),font_size=12)
```


```{r DiffExprProteo3,echo=FALSE, message=FALSE, warning=FALSE,  fig.show = "hold", out.width = "80%", echo=FALSE}

DEF_mat <- FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$DiffExpAnal[["mergeDEF"]]
UpSetR::upset(DEF_mat, sets = (names(DEF_mat[,-1]))) 
```


```{r DiffPerContProteo, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE}

  out <- NULL
  
  for (contrast  in  FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]][["contrasts"]]$contrastName) {
    
      out <- c(out, knitr::knit_child("DiffExpAnal_PerContrast.Rmd", quiet=TRUE))  
      
    }
    
knitr::asis_output(out)

```

`r  if(isFALSE(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$results))  {"\\end{comment}"}`


## Co-expression

Co-expression analysis was carried out on the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$merge.type`
of the following list of proteins `r FlomicsMultiAssay[[paste0(data,".filtred")]]@metadata$CoExpAnal$gene.list.names`. 
`r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$tools` was
used to cluster genes. 
The gaussian mixture models was run on filtered (meanFilterCutoff was set to: `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$meanFilterCutoff`), 
normalised (normalisation method was `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$normFactors`) 
and transformed (transformation method: `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$transformation`) count data.
X technical replicates were performed from $K=i$ to $K=i$ (K=number of clusters). 
The best number of cluster (K) selected via the Integrated Completed Likelihood (ICL) criterion 
was `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$cluster.nb`.



```{r CoexpProt, message=FALSE, warning=FALSE, echo=FALSE, message=TRUE, warning=TRUE}

  out <- NULL
 
      out <- c(out, knitr::knit_child("CoExpAnal.Rmd", quiet=TRUE))  
    
knitr::asis_output(out)

```

`r  if(isFALSE(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$results)) {"\\end{comment}"}`

