## Differential expression analysis

Differential expression analysis was carried out for each selected contrast thanks to the `r dataset.SE@metadata[["DiffExpAnal"]]$method` model. 

P-value of differential expressed `r omics.dic[[omictype]][["variableName"]]` were adjusted according to the `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.method` method
with a cutoff set to `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.cutoff`.

### Summary

```{r ,echo=FALSE,message=FALSE, out.width = "100%",warning=FALSE,  fig.show = "hold", eval=Diff.eval}

tmpRes <- dataset.SE@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:dim(tmpRes[["contrasts"]])[1]){
   contrastName <- tmpRes[["contrasts"]][i,]$contrastName
   #hyp <- tmpRes[["contrasts"]][i,]$tag
   stats <- tmpRes[["stats"]][[contrastName]]
   DE[i] <- stats$gDE
   DEup[i] <- paste(stats$gDEup,"(",stats$pgDEup," %)",sep="")
   DEdown[i] <- paste(stats$gDEdown,"(",stats$pgDEdown," %)",sep="")
}

```


```{r , echo=FALSE, results="asis", eval=Diff.eval}
kable_styling(kable(bind_cols(tmpRes[["contrasts"]][,c("tag","contrastName")], data.frame("Nb DE"=DE,"Nb DEup"=DEup,"Nb DEdown"=DEdown)), row.names=FALSE, caption=NULL, format="html"), font_size=12)

```


The following graph gives the number of common and specific differential expressed `r omics.dic[[omictype]][["variableName"]]` per testing hypothesis.


```{r ,echo=FALSE, message=FALSE, warning=FALSE, fig.show = "hold", out.width = "80%", echo=FALSE, eval=Diff.eval}
DEF_mat <- dataset.SE@metadata$DiffExpAnal[["mergeDEF"]]

if(dim(DEF_mat)[2] > 2){
  UpSetR::upset(DEF_mat, sets = (names(DEF_mat[,-1]))) 
}
```

<!-- ### Results per contrast -->

```{r , message=FALSE, warning=FALSE, echo=FALSE, eval=Diff.eval}

  out <- NULL
  
  for (contrast  in  dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]]$contrastName) {
      out <- c(out, knitr::knit_child(paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_04_diff_analysis_per_contrast.Rmd"), quiet=TRUE))  
      
    }
    
knitr::asis_output(out)
```