## Co-expression {.tabset}

```{r , echo=FALSE , message=FALSE, warning=FALSE}
coexpDir <- paste0(dataDir,"/","03-Coexpression_analysis/")
dir.create(path=coexpDir)

knitr::opts_chunk$set(
  fig.path=coexpDir
)
```


Co-expression analysis was carried out on the `r dataset.SE@metadata[["CoExpAnal"]]$merge.type`
of the following list of `r omics.dic[[omictype]][["variableName"]]`  `r dataset.SE@metadata$CoExpAnal$gene.list.names`. 
`r dataset.SE@metadata[["CoExpAnal"]]$tools` was used to cluster the `r omics.dic[[omictype]][["variableName"]]`. 
The gaussian mixture model was run on filtered (meanFilterCutoff was set to: `r dataset.SE@metadata[["CoExpAnal"]]$meanFilterCutoff`), 
normalised (normalisation method was `r dataset.SE@metadata[["CoExpAnal"]]$normFactors`) 
and transformed (transformation method: `r dataset.SE@metadata[["CoExpAnal"]]$transformation`) count data.
`r dataset.SE@metadata[["CoExpAnal"]]$replicates.nb` technical replicates were performed for each K in `r dataset.SE@metadata[["CoExpAnal"]]$K.range` (K=number of clusters). 
The best number of cluster (K) selected via the Integrated Completed Likelihood (ICL) criterion 
was `r dataset.SE@metadata[["CoExpAnal"]]$cluster.nb`.


### ICL 


```{r ICL, echo=FALSE}
plot.coseq.res <- dataset.SE@metadata[["CoExpAnal"]]$plots
par(mar = c(4, 4, .5, .1))
plot.coseq.res$ICL 
```

### boxplots

```{r boxplots_profile, echo=FALSE}
par(mar = c(4, 4, .5, .1))
plot.coseq.res$boxplots
```

### probapost_boxplots 

```{r boxplots_proba, echo=FALSE}
par(mar = c(4, 4, .5, .1))
plot.coseq.res$probapost_boxplots 
```

### probapost_barplots

```{r barplots_probapost, echo=FALSE}
par(mar = c(4, 4, .5, .1))
plot.coseq.res$probapost_barplots
```


```{r export,echo = FALSE}
tab.clusters <- as.data.frame(ifelse(dataset.SE@metadata$CoExpAnal$coseqResults@allResults[[dataset.SE@metadata$CoExpAnal$cluster.nb]] > 0.5, 1,0))
tab.clusters <-  rownames_to_column(tab.clusters,var="DEF")
      
write.table(tab.clusters,
             file=paste0(coexpDir,"Table_of_DE_",omics.dic[[omictype]][["variableName"]],"_per_cluster",".txt"),
             sep="\t",quote=FALSE,col.names=TRUE,row.names=FALSE)

```
