## Annotation and Enrichment : `r annot`

```{r , echo=FALSE , message=FALSE, warning=FALSE}
annotDir <- paste0(dataDir,"/","04-Enrichment_analysis/")
dir.create(path=annotDir)

knitr::opts_chunk$set(
  fig.path=annotDir
)
```

Analyses in this part are conducted using the clusterprofiler R-package. 

### Summary

```{r , message=FALSE, warning=FALSE, echo=FALSE}
overview_list <- lapply(dataset.SE@metadata[[annot]][["results_CPR"]], FUN = function(contrasts_res){
  res_inter <- lapply(contrasts_res, FUN = function(list_CPR){
    if(!is.null(list_CPR)) return(nrow(list_CPR@result[list_CPR@result$p.adjust < list_CPR@pvalueCutoff,]))
    else return(0)
  })
  names(res_inter) <- names(contrasts_res)
  res_inter
})
names(overview_list) <- names(dataset.SE@metadata[[annot]][["results_CPR"]])

dt_res <- as.data.frame(do.call("rbind", overview_list))
dt_res <- dt_res %>% dplyr::mutate(Contrast = rownames(dt_res)) %>% dplyr::relocate(Contrast)
```

`r nrow(dt_res)` lists of genes have been analyzed for enrichment using `r dataset.SE@metadata[[annot]][["results_CPR_input"]]$dom.select` annotation. 
`r if(length(grep("GO", dataset.SE@metadata[[annot]][["results_CPR_input"]]$dom.select))!=0){paste0("Using", dataset.SE@metadata[[annot]][["results_CPR_input"]]$db, " to do the analysis")}`.

Adjusted pvalue was set to `r dataset.SE@metadata[[annot]][["results_CPR_input"]]$pvalueCutoff`.

```{r , message=FALSE, warning=FALSE, echo=FALSE}
DT::datatable(dt_res, rownames = FALSE, options = list(pageLength = 10))
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}

  out <- NULL

  for (listname  in names(dataset.SE@metadata[[annot]]$results_CPR)){
      for(domain in names(dataset.SE@metadata[[annot]]$results_CPR[[listname]])){
      out <- c(out, knitr::knit_child(paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_06_annot_enrich_per_list_per_Domain_CPR.Rmd"), quiet=TRUE))
  }
}
    
knitr::asis_output(out)

```



