---
title: "`r params$title`"
author: "Analysis were performed by the RFLOMICS package (cite)"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d %B %Y - %H:%M')`"
bibliography: bibliography.bib
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    theme: flatly
params: 
  outDir: NA
  FEdata: NA
  title: NA
---


```{r , include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, error = TRUE)
options(knitr.duplicate.label = "allow")
```

```{r library}

library(RFLOMICS)
```


```{r parameters, include=FALSE}

load(params$FEdata)
outDir <- params$outDir
projectName <- params$title

```

```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Create a directory to store all the results (tables and figures) of the project in a tmpdir
# user may download this results as an archive from the shiny interface
dir.create(path = outDir, showWarnings = FALSE)
```

<!-- enable to zoom by clicking on graphs in the report -->

```{css zoom-lib-src}
### ZOOM 
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery}
$(document).ready(function() {
$('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
// onClick function for all plots (img's)
$('img:not(.zoomImg)').click(function() {
$('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
$('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
});
// onClick function for zoomImg
$('img.zoomImg').click(function() {
$('.zoomDiv').css({opacity: '0', width: '0%'}); 
});
});
```

<!-- Experimental design -->

```{r design}

out <- NULL
child <- paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_02_design.Rmd")
out <- c(out, knitr::knit_child(child, quiet=TRUE))  

knitr::asis_output(out)

```

<!-- single omics analysis -->

```{r analysis, eval=(length(getOmicsTypes(rflomics.MAE)) != 0 )}

out <- NULL
omicsData <- getOmicsTypes(rflomics.MAE)
for (omictype in unique(omicsData)){ 
  
  for (data in  names(omicsData[omicsData == omictype])){
    
    child <- paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_01_omics.Rmd") 
    out   <- c(out, knitr::knit_child(child, quiet=TRUE))  
  }
}

knitr::asis_output(out)

```

<!-- data integration  -->

<!-- ## with MOFA -->

`r if(is.null(rflomics.MAE@metadata$IntegrationAnalysis$MOFA)) {"\\begin{comment}"}`

---

# MOFA2 Integration

`r if(is.null(rflomics.MAE@metadata$IntegrationAnalysis$MOFA)) {"\\end{comment}"}`

```{r MOFA2, eval = !is.null(rflomics.MAE@metadata$IntegrationAnalysis$MOFA), hide = is.null(rflomics.MAE@metadata$IntegrationAnalysis$MOFA) }

out <- NULL

out <- c(out, knitr::knit_child(paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_07_MOFA2_integration.Rmd"), quiet=TRUE))

knitr::asis_output(out)

```

<!-- ## with MixOmics -->

`r if(is.null(RFLOMICS::getMixOmics(rflomics.MAE))) {"\\begin{comment}"}`

---

# MixOmics Integration

`r if(is.null(RFLOMICS::getMixOmics(rflomics.MAE))) {"\\end{comment}"}`

```{r, eval = !is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics), hide = is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics)}
MOres <- NULL
funcMixo <- NULL
MOres <- RFLOMICS::getMixOmicsSettings(rflomics.MAE)
funcMixo <- ifelse(MOres$sparsity, "splsda",  "plsda")
funcMixo <- ifelse(length(MOres$selectData) > 1, paste0("block.", funcMixo), funcMixo)
```

```{r , eval = !is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics), hide = is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics) }
htmltools::HTML(paste0("MixOmics analyses were performed on <span style=\"color:blue\">",  
                       paste(MOres$selectData, collapse = ", "), 
                       "</span> datatables with function  <span style=\"color:DarkOrchid\">", 
                       funcMixo, 
                       "</span> applied on each selected response variable (<span style=\"color:blue\">",
                       paste(MOres$selectedResponse, collapse = ", "), 
                       "</span>). Option <span style=\"color:blue\"> scale views </span> was set to", 
                       MOres$scale_views, "."))
```

```{r , eval = !is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics), hide = is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics), results="asis"}
listSel <- NULL
listSel <- MOres$selectionMethod

listSel2 <- lapply(names(listSel),  FUN = function(nam) {
    dat <- listSel[[nam]]
    varNam <- RFLOMICS:::.omicsDic(rflomics.MAE, SE.name = nam)$variableName
    switch(dat[1], 
           "diff" = {
               paste0("Only differentially expressed ", 
                      varNam, 
                      " were processed in the multi-omics analysis, taking the ", 
                      ifelse(dat[2], "union", "intersection"), " of all contrasts lists.")
           },
           "none" = paste0("No features selection was applied, all ",
                           varNam,
                           " were taken into account."))
})
names(listSel2) <- names(listSel)

for (nam in names(listSel2)) {
    cat("* ", nam, ": ", listSel2[[nam]], "\n")
}
rm(listSel, listSel2)
```


```{r mixOmics, eval = !is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics), hide = is.null(rflomics.MAE@metadata$IntegrationAnalysis$mixOmics) }

if (MOres$sparsity) {
    htmltools::HTML(paste0("Sparse analysis was performed on these data with <span style=\"color:blue\">",  
                           MOres$cases_to_try, 
                           "</span> sets of features tested for each datatable."))
}

out <- NULL
for (selectedResponse in MOres$selectedResponse) { 
  
  child <-  paste0(path.package("RFLOMICS"), 
                   "/RFLOMICSapp/",
                   "report_08_mixOmics_integration.Rmd") 
  
  out <- c(out, knitr::knit_child(child, quiet = TRUE))  
}

knitr::asis_output(out)

```

---

# R Session

See **session_info.txt** files in the results directory.

```{r session, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE}
writeLines(capture.output(devtools::session_info()),  
           paste0(outDir,"/","session_info.txt"))
```


# Bibliographie

<div id="refs"></div>


