# Experimental design

User-provided experimental plan.

```{r design}

bioFact   <- getBioFactors(rflomics.MAE)
batchFact <- getBatchFactors(rflomics.MAE)
metaFact  <- getMetaFactors(rflomics.MAE)

DT::datatable(getDesignMat(rflomics.MAE)[c(bioFact, batchFact, metaFact)], 
              options = list(rownames = FALSE, pageLength = 6, scrollX = T, dom = 'tip'),
              class = 'cell-border stripe')

              # caption = htmltools::tags$caption(style = 'caption-side: top;
              #                                   text-align: left;
              #                                   color:black;
              #                                   font-size:20px;
              #                                   font-weight: bold;', "User-provided experimental plan"),
```

Overview of the input omic data. Each color represents a distinct dataset, with their respective samples on the x-axis and the number of features on the y-axis. It illustrates the samples overlap across dataset.

```{r data.over.view, fig.show = "hold", out.width = "70%", fig.align='left'}

raw.rflomics.MAE <- subRflomicsMAE(rflomics.MAE, omicNames = paste0(getDatasetNames(rflomics.MAE), ".raw"))
names(raw.rflomics.MAE) <- getDatasetNames(rflomics.MAE)
plotDataOverview(object = raw.rflomics.MAE)

```

Number of Datasets per Condition. Each axis represents a distinct biological factor, and each cell value signifies the count of datasets associated with that specific condition.

```{r condition.over.view, fig.show = "hold", out.width = "60%", fig.align='left'}

plotConditionsOverview(object = raw.rflomics.MAE)

```


# Statstical setting:

The selected references and types of factors.

```{r factors, echo=FALSE, message=TRUE, warning=TRUE}

fact.types <- getFactorTypes(rflomics.MAE)
fact.names <- getFactorNames(rflomics.MAE)
fact.ref <- vector()
for(i in 1:length(fact.names)){
  fact.ref[i] <- getFactorModalities(rflomics.MAE, fact.names[i])[1]
}

df <- data.frame("Factor_names" = fact.names ,
           "Factor_type" = fact.types,
           "Factor_reference" = fact.ref)

DT::datatable(df , rownames = FALSE , class = 'cell-border stripe',
              options = list( pageLength = 6, scrollX = F, dom = 'tip'))

# caption= htmltools::tags$caption(style = 'caption-side: top;
#                                                 text-align: left;
#                                                 color:black;
#                                                 font-size:20px;
#                                                 font-weight: bold;', "Factor settings")
```


<p>The selected model formula.</p>

```
`r getModelFormula(rflomics.MAE)`
````

<p>The selected contrasts.</p>

```{r contrastSel, results="asis"}

df <- getSelectedContrasts(rflomics.MAE)[,c("groupComparison", "contrastName", "type")]
names(df) <- c("Comparison", "Contrasts", "Type")
DT::datatable(df, rownames = FALSE,
              options = list( pageLength = 6, scrollX = F, dom = 'tip'),
              class = 'cell-border stripe')
```


