<br>

## `r paste0("4.",num, " ", data)` 

```{r}
# create export data
opts_chunk$set(
  fig.path=diffDir[[data]]
)

dataset.SE     <- getRflomicsSE(rflomics.MAE, data)
validContrasts <- getValidContrasts(dataset.SE)
omicsType      <- getOmicsTypes(dataset.SE)
variableName   <- RFLOMICS:::.omicsDic(dataset.SE)[["variableName"]]
```

<!-- ## Summary table of differential expression analysis -->

* **Methods:**

`r if(omicsType != "RNAseq") {"\\begin{comment}"}`

The **edgeR R-package** (version `r RFLOMICS:::.getPackageInfo(rflomics.MAE, "edgeR")`) (@robinson2010a) was used to performed the analysis. 
First, the parameters of the generalized linear model were estimate thanks to the 
estimateGLMCommonDisp(), estimateGLMTrendedDisp(), estimateGLMTagwiseDisp() and glmFit() functions.
Then, the likelihood ratio test(s) (LRT) were performed for each contrast thanks to the glmLRT() 
function.

`r if(omicsType != "RNAseq") {"\\end{comment}"}`

`r if(omicsType == "RNAseq") {"\\begin{comment}"}`

The **limma R-package** (version `r RFLOMICS:::.getPackageInfo(rflomics.MAE, "limma")`) (ref) was used to performed the analysis.
First, the parameters of the linear model were estimated thanks to lmFit() function.
In a second time, contrasts.fit was used and empirical bayes statistics were obtained thanks to the eBayes() functions.

`r if(omicsType == "RNAseq") {"\\end{comment}"}`

P-values of differential expressed `r variableName` were adjusted according 
to the **`r getDiffSettings(dataset.SE)$p.adj.method`** procedure with a **cutoff** set to **`r getDiffSettings(dataset.SE)$p.adj.cutoff`**.
**LogFC cut-off** was set to **`r getDiffSettings(dataset.SE)$abs.logFC.cutoff`**.

<br>

###  {.tabset}

* **Summary of the results for all the contrasts:**

#### Intersection

```{r Upset_plot, fig.show = "hold", out.width = "100%", fig.cap=paste0("<p style=\"color:grey\">","*fig: This **UpSetR** plot gives the number of common and specific differential expressed ",variableName," per contrasts.*", "</p>")}

DEF_mat <- as.data.frame(dataset.SE@metadata$DiffExpAnal[["mergeDEF"]])
DEF_mat <- DEF_mat[c("DEF", validContrasts$contrastName)]

write.table(DEF_mat, file=paste0(diffDir[[data]],"/","Matrice_of_DE_", variableName,"_per_Constrast.txt"), sep="\t",quote=FALSE,col.names=TRUE,row.names=FALSE)

names(DEF_mat) <- 
  c(names(DEF_mat)[1], validContrasts$tag)

if(dim(DEF_mat)[2] > 2){
  upset(DEF_mat, sets = (names(DEF_mat[,-1])), order.by = "freq") 
}

```

#### Stat summary
```{r , echo=FALSE, results="asis", fig.cap=paste0("<p style=\"color:grey\">","*tab: ???.*", "</p>")}

tmpRes <- dataset.SE@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:nrow(tmpRes[["contrasts"]])){
  contrastName <- tmpRes[["contrasts"]][i,]$contrastName
  stats <- tmpRes[["stats"]][contrastName,]
  DE[i] <- stats[["All"]]
  DEup[i] <- 
    paste(stats[["Up"]]," (",round(stats[["Up"]]/stats[["All"]],2)*100," %)",sep="")
  DEdown[i] <- 
    paste(stats[["Down"]]," (",round(stats[["Down"]]/stats[["All"]],2)*100," %)",sep="")
}

stat_summary <- cbind(tmpRes[["contrasts"]][,c("tag","contrastName")],
                       data.frame("DE.Tot"=DE,"DE.Up"=DEup,"DE.Down"=DEdown))

write.table(stat_summary, file=paste0(diffDir[[data]],"summay_stat.txt"),
              sep="\t", quote=FALSE, col.names=T, row.names=F)

noValidContrasts <- 
  setdiff(stat_summary$contrastName, validContrasts$contrastName)

if(length(noValidContrasts) !=0){
  
  datatable(stat_summary, rownames = FALSE , class = 'cell-border stripe',
              options = list( pageLength = 6, scrollX = F, dom = 'tip')) |>
  formatStyle(
      "contrastName", target = 'row', 
      color = styleEqual(noValidContrasts, 'red')
    )
}else{
  datatable(stat_summary, rownames = FALSE , class = 'cell-border stripe',
              options = list( pageLength = 6, scrollX = F, dom = 'tip'))
}


```

`r if(length(noValidContrasts) !=0) {"<p style=\"color:red;\">*Red: No differentially expressed features or contrasts not validated by the user.*</p>"}`

### {-}

<br>

* **Display results by contrast(s):** 

*Please click on the arrows to scroll down the results and click on the figure to zoom*

```{r, results='asis'}

out <- NULL

for (contrast  in  getValidContrasts(dataset.SE)$contrastName) {
#for (contrast  in  getSelectedContrasts(dataset.SE)$contrastName) {
  
  tag <- stat_summary[which(stat_summary$contrastName == contrast),]$tag
  out <- c(out, knit_child(
    paste0(path.package("RFLOMICS"),"/RFLOMICSapp/",
           "report_04_diff_analysis_per_contrast.Rmd"), quiet=TRUE)) 
}

asis_output(out)
```

