---
title: "`r FlomicsMultiAssay@metadata$projectName` project"
author: "Analyzes performed by RFLOMICS package"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: bibliography.bib
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
    theme: united
params: 
  pngDir: NA
  FEdata: NA
---


```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r library, echo=FALSE, message=FALSE, warning=FALSE}

library(RFLOMICS)
library(dplyr)
library(ggplot2)
library(DT)
library(reactable)

```


```{r parameters, include=FALSE}

load(params$FEdata)
pngDir <- params$pngDir

```

# Design
## Experimental plan

<!-- ## Sample sheet overview -->

```{r Design, echo=FALSE, message=TRUE, warning=TRUE}

DT::datatable(as.data.frame(FlomicsMultiAssay@colData), 
              options = list(rownames = FALSE, pageLength = 6, scrollX = T, dom = 'tip'),
              class = 'cell-border stripe')

```


```{r factors, echo=FALSE, message=TRUE, warning=TRUE}

Bio.fact   <- FlomicsMultiAssay@metadata$design@Factors.Type[FlomicsMultiAssay@metadata$design@Factors.Type == "Bio"]
Batch.fact <- FlomicsMultiAssay@metadata$design@Factors.Type[FlomicsMultiAssay@metadata$design@Factors.Type == "batch"]

```

* `r paste0("Biological factor : ",  paste0(names(Bio.fact), collapse = ", "))`
* `r paste0("Batch factor : ",  paste0(names(Batch.fact), collapse = ", "))`

## Omics data

```{r Sample table, echo=FALSE, fig.show = "hold", out.width = "70%", message=FALSE, warning=FALSE}

loaded.data <- data.frame(datasets = sapply(names(FlomicsMultiAssay@metadata$omicList), 
                              function(x){ paste0(FlomicsMultiAssay@metadata$omicList[[x]], collapse = ", ") }), 
                          omics = names(FlomicsMultiAssay@metadata$omicList)) %>% as.data.table()

DT::datatable(loaded.data, 
              options = list(rownames = FALSE, pageLength = 10, scrollX = T, dom = 'tip'),
              class = 'cell-border stripe')

# kable_styling(kable(loaded.data, row.names=FALSE, caption=NULL, format="html"), font_size=12,full_width = F, position = "left")

```


```{r upsetSamples, echo=FALSE, fig.show = "hold", out.width = "70%", message=FALSE, warning=FALSE}


if(length(unlist(FlomicsMultiAssay@metadata$omicList)) > 2){
  
  upsetSamples(FlomicsMultiAssay[unlist(FlomicsMultiAssay@metadata$omicList),])
}


#check <- CheckExpDesignCompleteness(FlomicsMultiAssay)

#check$plot
```

## Statistical model

* The statistical model written for the experiment is:  

```
`r FlomicsMultiAssay@metadata$design@Model.formula`
```

* The selected contrast(s) is (are):

```{r contrastSel, echo=FALSE, results="asis", warning=FALSE, message=FALSE}

DT::datatable(FlomicsMultiAssay@metadata$design@Contrasts.Sel[,c(5,2:3)], 
              options = list(rownames = FALSE, pageLength = 6, scrollX = T, dom = 'tip'),
              class = 'cell-border stripe')

# kable_styling(kable(FlomicsMultiAssay@metadata$design@Contrasts.Sel[,c(5,2:3)], 
#                     row.names=FALSE, caption=NULL, format="html"), font_size=12,full_width = F, position = "left")
```

`r if(length(FlomicsMultiAssay@metadata$omicList) ==0 ) {"\\begin{comment}"}`

```{r analysis, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE}

  out <- NULL
  for (omictype in names(FlomicsMultiAssay@metadata$omicList)){ 
    
    # child <- paste0("report_",omictype, ".Rmd")
    child <-  paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","report_",omictype, ".Rmd") 

    for (data in  FlomicsMultiAssay@metadata$omicList[[omictype]]){
      
      out <- c(out, knitr::knit_child(child, quiet=TRUE))  
    }
    
  }

knitr::asis_output(out)

```

`r if(length(FlomicsMultiAssay@metadata$omicList) == 0 ) {"\\end{comment}"}`

```{r , message=FALSE, warning=FALSE, echo=FALSE, eval = !is.null(FlomicsMultiAssay@metadata$MOFA_results), hide = is.null(FlomicsMultiAssay@metadata$MOFA_results) }

  out <- NULL
  
  out <- c(out, knitr::knit_child(paste0(path.package("RFLOMICS"), "/RFLOMICSapp/","MOFA2_integration.Rmd"), quiet=TRUE))
    
knitr::asis_output(out)

```

# R Session

```{r session, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE}
devtools::session_info()
```


# Bibliographie


