
```{r MOFA_chunkoptions, include = FALSE, hide = TRUE, eval = TRUE}
explorDir <- paste0(outDir,"/","Integration/MOFA2/")
dir.create(path = explorDir)

knitr::opts_chunk$set(fig.path = explorDir)
```

```{r MOFA_extract}
MOFARes <- rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]][["MOFA_results"]]
```

## Settings

* MOFA2  R package was used to perform data unsupervised integration, on <span style="color:blue">`r paste(MOFA2::views_names(MOFARes), collapse = ", ")`</span> datatables.
* Selected contrasts: `r cat(paste(paste0("\t [*] ", rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_selected_contrasts), collapse = " \n "))` 

<!-- TODO The above does not work... -->
* Taking the <span style="color:blue">`r rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_selected_filter`</span> of lists of DE features lead to the following analysis setting: 

```{r MOFA2_data_overview, fig.width=6.5, fig.height = 5, fig.align="center"}
MOFA2::plot_data_overview(MOFARes)
```

* Options for the run:
  * Scale views: `r rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_untrained@data_options$scale_views` 
  * Number of factors: `r rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_untrained@model_options$num_factors` 
  * Number of iterations: `r rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_untrained@training_options$maxiter` 
* RNASeq data were transformed using <span style="color:DarkOrchid">voom</span> transformation from limma package 
* Batch effects`r rflomics.MAE@metadata$IntegrationAnalysis[["MOFA"]]$MOFA_untrained@training_options$maxiter`  were corrected using <span style="color:DarkOrchid">removebatcheffect</span> function from limma package.

##  Results


### Correlation between factors

```{r}
mat_cor <- stats::cor(MOFA2::get_factors(MOFARes)[[1]])
mat_cor <- mat_cor - diag(mat_cor)
```

* Number of computed factors: `r MOFARes@dimensions$K` 
* Is there a correlation >0.5 between two factors? `r ifelse(any(mat_cor>0.5), "YES, be careful, the results are unreliable.", "No.")`

```{r MOFA2_factor_cor, fig.width=4.5, fig.height = 4, fig.align="center"}
MOFA2::plot_factor_cor(MOFARes)
```

### Explained Variance

```{r explained_variance, fig.width = 10, fig.height = 4, fig.align = "center"}
g1 <- MOFA2::plot_variance_explained(MOFARes, plot_total = TRUE)[[2]] + # compute both per factor and per table by default.
  ggplot2::ggtitle("Total explained variance per omic data")
g2 <- MOFA2::plot_variance_explained(MOFARes, x = "view", y = "factor") + ggplot2::ggtitle("Explained variance by factors and omic data")

ggpubr::ggarrange(g1, g2, ncol = 2)
```

### Weights of the factors explaining the most variance

The following image shows the weights of the features for each table and each factors for all factors that explain at least 5\% of the variance in any table. 

```{r}
VarExp = MOFA2::get_variance_explained(MOFARes)$r2_per_factor$group1
FactNum = apply(VarExp, 1, FUN = function(vect) any(vect > 5)) # Percentage
f.height = 5 + 2*length(which(FactNum))
f.width  = 5 + 2*length(MOFA2::views_names(MOFARes))
```

```{r, fig.height = f.height, fig.width=f.width, fig.align = "center"}
ggplot_list <- list()
for (i in which(FactNum)) {
  for (j in MOFA2::views_names(MOFARes)) {

        ggplot_list[[length(ggplot_list) + 1]] <- MOFA2::plot_top_weights(MOFARes,
                                                         view = j,
                                                         factors = i,
                                                         nfeatures = 10, 
                                                         scale = TRUE) + ggplot2::ggtitle(paste0(j, " - Factor ", i))
  }
}

ggpubr::ggarrange(plotlist = ggplot_list,
                  ncol = length(MOFA2::views_names(MOFARes)),
                  nrow = length(FactNum[FactNum]))
```

### Heatmaps

For all views, these heatmap show the 10 first features in term of weights for the first and second factors.

```{r, fig.width = 15, fig.height = 5, fig.show = "hide"}
list_heat_views = list()
for (nam in MOFA2::views_names(MOFARes)) {
  list_heat_views[[nam]] <- list()
  list_heat_views[[nam]][[1]] <- MOFA2::plot_data_heatmap(MOFARes, view = nam, factor = 1, features = 10, main = paste0(nam, " - Factor 1"), cellheight = 20, cellwidth = 12)$gtable
  list_heat_views[[nam]][[2]] <- MOFA2::plot_data_heatmap(MOFARes, view = nam, factor = 2, features = 10, main = paste0(nam, " - Factor 2"), cellheight = 20, cellwidth = 12)$gtable
}
```

```{r MOFA2_heatmaps, fig.width = 12, fig.height = 7}
res <- lapply(list_heat_views, FUN = function(liste){
  gridExtra::grid.arrange(grobs = liste, ncol = 2)
})
```

```{r MOFA2_export}
write.table(MOFA2::get_factors(MOFARes, as.data.frame = TRUE),
             file = paste0(explorDir, "Factors_values.txt"),
             sep = "\t", quote = FALSE, col.names = TRUE, row.names = TRUE)
write.table(MOFA2::get_weights(MOFARes, as.data.frame = TRUE),
             file = paste0(explorDir, "Factors_weights.txt"),
             sep = "\t", quote = FALSE, col.names = TRUE, row.names = TRUE)
```

