## Differential expression analysis

```{r , echo=FALSE , message=FALSE, warning=FALSE}
# create export data
anaDiffDir <- paste0(dataDir,"/","02-Diff_Expression_results/")
dir.create(path=anaDiffDir)

knitr::opts_chunk$set(
  fig.path=anaDiffDir
)

```

<!-- ## Summary table of differential expression analysis -->

Differential expression analysis was carried out for each selected contrast thanks to the `r dataset.SE@metadata[["DiffExpAnal"]]$method` model. 

P-values of differential expressed `r omics.dic[[omictype]][["variableName"]]` were adjusted according to the `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.method` procedure with a cutoff set to `r dataset.SE@metadata[["DiffExpAnal"]]$Adj.pvalue.cutoff`.


* **Summary of differential expression analysis**

```{r ,echo=FALSE,message=FALSE, out.width = "100%",warning=FALSE,  fig.show = "hold", eval=Diff.eval}

tmpRes <- dataset.SE@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:dim(tmpRes[["contrasts"]])[1]){
   contrastName <- tmpRes[["contrasts"]][i,]$contrastName
   #hyp <- tmpRes[["contrasts"]][i,]$tag
   stats <- tmpRes[["stats"]][[contrastName]]
   DE[i] <- stats$gDE
   DEup[i] <- paste(stats$gDEup,"(",stats$pgDEup," %)",sep="")
   DEdown[i] <- paste(stats$gDEdown,"(",stats$pgDEdown," %)",sep="")
}

```


```{r , echo=FALSE, results="asis", eval=Diff.eval}
kable_styling(kable(bind_cols(tmpRes[["contrasts"]][,c("tag","contrastName")], data.frame("#DE"=DE,"#DEup"=DEup,"# DEdown"=DEdown)), row.names=FALSE, caption=NULL, format="html"), font_size=12)
```


The following graph gives the number of common and specific differential expressed `r omics.dic[[omictype]][["variableName"]]` per testing hypothesis.


```{r Upset_plot,echo=FALSE, message=FALSE, warning=FALSE, fig.show = "hold", out.width = "80%", echo=FALSE, eval=Diff.eval}

DEF_mat <- dataset.SE@metadata$DiffExpAnal[["mergeDEF"]]

if(dim(DEF_mat)[2] > 2){
  UpSetR::upset(DEF_mat, sets = (names(DEF_mat[,-1]))) 
}

write.table(DEF_mat, file=paste0(anaDiffDir,"/","Matrice_of_DE_",omics.dic[[omictype]][["variableName"]],"_per_Constrast.txt"), sep="\t",quote=FALSE,col.names=TRUE,row.names=FALSE)

```

* **Results by contrast(s):** 

*Please click on the arrows to scroll down the results and click on the figure to zoom*

```{r , message=FALSE, warning=FALSE, echo=FALSE, eval=Diff.eval}

out <- NULL
  
  for (contrast  in  dataset.SE@metadata[["DiffExpAnal"]][["contrasts"]]$contrastName) {
      out <- c(out, knitr::knit_child(paste0(path.package("RFLOMICS"),"/RFLOMICSapp/","report_04_diff_analysis_per_contrast.Rmd"), quiet=TRUE))  
      
    }
    
knitr::asis_output(out)
```
