## Data pre-processing and QC: {.tabset}

<br>

```{r , echo=FALSE , message=FALSE, warning=FALSE}
# create export data
explorDir <- paste0(dataDir,"/","01-Exploratory_analysis/")
dir.create(path=explorDir)

knitr::opts_chunk$set(
  fig.path=explorDir
)


```


```{r check-design, echo=FALSE , message=FALSE, warning=FALSE, echo=FALSE, out.width = "75%"}

dataset.raw.SE <- rflomics.MAE@ExperimentList[[data]]
dataset.SE     <- rflomics.MAE@ExperimentList[[paste0(data,".filtred")]]

# 
check <- CheckExpDesignCompleteness(rflomics.MAE, colnames(rflomics.MAE[[paste0(data,".filtred")]]))
check$plot
           
```

`r if(length(colnames(dataset.raw.SE)) - length(colnames(dataset.SE)) == 0) {"\\begin{comment}"}`

* The *outlier samples* are removed: `r setdiff(colnames(dataset.raw.SE), colnames(dataset.SE))`.

`r if(length(colnames(dataset.raw.SE)) - length(colnames(dataset.SE)) == 0) {"\\end{comment}"}`

<!-- RNAseq data cas -->

`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\begin{comment}"}`

* By default, the *unexpressed genes* were filtered-out (`r length(dataset.raw.SE@metadata$rowSums.zero)` genes).
* Then, *low expressed genes* were filtered-out using the *cpm* (counts per million) method. *Genes* with a cpm
lower to `r dataset.SE@metadata$FilteringOptions$CPM_Cutoff` in at least "`r dataset.SE@metadata$FilteringOptions$Filter_Strategy`" were filtered out ( `r length(dataset.raw.SE@metadata$FilteredFeatures)` genes).

* The calcNormFactors function of the R-package edgeR `r dataset.SE@metadata$Normalization$methode` normalization method was applied. 

`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\end{comment}"}`

<!-- proteomics or metabolomics data cas -->

`r if(dataset.raw.SE@metadata$omicType == "RNAseq") {"\\begin{comment}"}`

* The data were transformed using `r rflomics.MAE@ExperimentList[[paste0(data,".filtred")]]@metadata$transform_method`.

`r if(dataset.raw.SE@metadata$omicType == "RNAseq") {"\\end{comment}"}`



```{r, echo=FALSE, message=TRUE, warning=TRUE, eval=FALSE}

# filt.summary <-  data.frame("Status"=c("raw dataset",
#                               "0 count",
#                               "low count",
#                               "filtered sataset"),
#                             "Number of gene"=c(length(names(dataset.raw.SE)),
#                               length(dataset.raw.SE@metadata$rowSums.zero),
#                               length(dataset.SE@metadata$FilteredFeatures),
#                               length(names(dataset.SE))))

DT::datatable(filt.summary, options = list(colnames=FALSE, rownames = FALSE, pageLength = 10, scrollX = T, dom = 'tip'),class = 'cell-border stripe')

```

<br>
<!-- Histograms of the library size before/after pre-processing -->

`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\begin{comment}"}`

### Library sizes:

```{r Library_size_barplot, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE, eval=(dataset.raw.SE@metadata$omicType == "RNAseq")}

Library_size_barplot.plot(dataset.raw.SE)

Library_size_barplot.plot(dataset.SE)

```

`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\end{comment}"}`

<!-- Distribution of feature counts before/after pre-processing : boxplot -->

### Feature counts (Boxplot):

```{r boxplot, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
Data_Distribution_plot(dataset.raw.SE, plot = "boxplot")
Data_Distribution_plot(dataset.SE, plot = "boxplot")
```

### Feature counts (density)

```{r density-plot, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
Data_Distribution_plot(dataset.raw.SE, plot = "density")
Data_Distribution_plot(dataset.SE, plot = "density")
```

### PCA

```{r PCA_1_2, echo=FALSE , fig.show="hold", message=FALSE, warning=FALSE, out.width = "50%"}

RFLOMICS::plotPCA(dataset.raw.SE, PCA="raw", PCs=c(1, 2), condition="groups")
RFLOMICS::plotPCA(dataset.SE, PCA="norm", PCs=c(1, 2), condition="groups")
```

```{r PCA_1_3, echo=FALSE , fig.show="hold", message=FALSE, warning=FALSE, out.width = "50%"}

RFLOMICS::plotPCA(dataset.raw.SE, PCA="raw", PCs=c(1, 3), condition="groups")
RFLOMICS::plotPCA(dataset.SE, PCA="norm", PCs=c(1, 3), condition="groups")
```


<br>

Quality control's graphs before and after the pre-processing:

`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\begin{comment}"}`
* Histogram of sample's library size
`r if(dataset.raw.SE@metadata$omicType != "RNAseq") {"\\end{comment}"}`
* Distribution of `r omics.dic[[omictype]][["valueType"]]` by sample
* Distribution of `r omics.dic[[omictype]][["valueType"]]` by sample
* Principal component analysis results: 
    + coordinates of samples on the axes 1 and 2
    + coordinates of samples on the axes 1 and 3



