
# `r data`  analysis

## Workflow of reference 

DiCoExpress [@Lambert:2020ta]

## Description of dataset's processing


```{r CheckDesign1, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
check <- CheckExpDesignCompleteness(Design, colnames(FlomicsMultiAssay[[paste0(data,".filtrered")]]))

NbGenes             <- length(names(FlomicsMultiAssay@ExperimentList[[data]]))
NbGene.rowSums.zero <- length(FlomicsMultiAssay@ExperimentList[[data]]@metadata$rowSums.zero)
NbGene.low.counts   <- length(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$FilteredFeatures)
```

### Filtering:

* By default, gene with 0 count are removed from the data. 
* The choosen filtering strategy is `r FlomicsMultiAssay[[paste0(data, ".filtred")]]@metadata$FilteringOptions$Filter_Strategy` with a count per million of read (CPM)
cut-off of `r FlomicsMultiAssay[[paste0(data, ".filtred")]]@metadata$FilteringOptions$CPM_Cutoff`  
* X samples were removed from the datasets.
* The number of genes: `r NbGenes`  
* Number of genes with zero count: `r NbGene.rowSums.zero`
* Number of genes filtered: `r NbGene.low.counts`

### Normalization:

The `r FlomicsMultiAssay[[paste0(data, ".filtred")]]@metadata$Normalization$methode` normalization method 
was applied and the scaling factors are stored in the table below:

```{r NormCoeff, echo=FALSE, results="asis"}
kable_styling(kable(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$Normalization$coefNorm, row.names=FALSE, caption=NULL, format="html"), font_size=12,full_width = F, position = "left")
```

### Distribution of library size befor/after processing

```{r libSize, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
Library_size_barplot.plot(FlomicsMultiAssay@ExperimentList[[data]])
Library_size_barplot.plot(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]])
```

### Distribution of density befor/after processing

```{r DensityPlot, echo=FALSE, fig.show = "hold", out.width = "50%", message=FALSE, warning=FALSE}
Data_Distribution_Density.plot(FlomicsMultiAssay@ExperimentList[[data]])
Data_Distribution_Density.plot(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]])
```


### Principal component analysis befor/after processing

```{r QCdesign, echo=FALSE , fig.show="hold", message=FALSE, warning=FALSE,out.width = "80%"}
#mvQCdesign(object = FlomicsMultiAssay,
#           data   = data, PCA="raw", axis=5, 
#           pngFile= NULL) 
mvQCdesign(object = FlomicsMultiAssay,
           data   = paste0(data,".filtred"), PCA="norm", axis=5, 
           pngFile= NULL) 
```



`r if(is.null(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]][["contrasts"]])) {"\\begin{comment}"}`

## Differential expression analysis

Differential expression analysis was carried out for each selected contrast thanks to the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$method` model. 

P-value of differential expressed genes were adjusted according to the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$Adj.pvalue.method` method
with a cutoff set to `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]$Adj.pvalue.cutoff`.

### Summary

```{r DiffExprRNA1,echo=FALSE,message=FALSE, out.width = "100%",warning=FALSE,  fig.show = "hold"}

tmpRes <- FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]]
DE <- vector()
DEup <- vector()
DEdown <- vector()

for (i  in  1:dim(tmpRes[["contrasts"]])[1]){
   contrastName <- tmpRes[["contrasts"]][i,]$contrastName
   #hyp <- tmpRes[["contrasts"]][i,]$tag
   stats <- tmpRes[["stats"]][[contrastName]]
   DE[i] <- stats$gDE
   DEup[i] <- paste(stats$gDEup,"(",stats$pgDEup," %)",sep="")
   DEdown[i] <- paste(stats$gDEdown,"(",stats$pgDEdown," %)",sep="")
}

```

```{r summaryRNADE, echo=FALSE, results="asis"}
kable_styling(kable(bind_cols(tmpRes[["contrasts"]][,c("tag","contrastName")], data.frame("Nb DE"=DE,"Nb DEup"=DEup,"Nb DEdown"=DEdown)), row.names=FALSE, caption=NULL, format="html"), font_size=12)
```


The following graph gives the number of common and specific differential expressed genes per testing hypothetis.

```{r DiffExprRNA2,echo=FALSE, message=FALSE, warning=FALSE,  fig.show = "hold", out.width = "80%", echo=FALSE}
DEF_mat <- FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata$DiffExpAnal[["mergeDEF"]]
UpSetR::upset(DEF_mat, sets = (names(DEF_mat[,-1]))) 
```


```{r DiffPerContRNA, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE}

  out <- NULL
  
  for (contrast  in  FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]][["contrasts"]]$contrastName) {
    
      out <- c(out, knitr::knit_child("DiffExpAnal_PerContrast.Rmd", quiet=TRUE))  
      
    }
    
knitr::asis_output(out)
```

`r if(is.null(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["DiffExpAnal"]][["contrasts"]])) {"\\end{comment}"}`

`r if(isFALSE(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$results))  {"\\begin{comment}"}`


## Co-expression

Co-expression analysis was carried out on the `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$merge.type`
of the following list of gene `r FlomicsMultiAssay[["RNAseq.set1.filtred"]]@metadata$CoExpAnal$gene.list.names`. 
`r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$tools` was
used to cluster genes. 
The gaussian mixture model was run on filtered (meanFilterCutoff was set to: `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$meanFilterCutoff`), 
normalised (normalisation method was `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$normFactors`) 
and transformed (transformation method: `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$transformation`) count data.
X technical replicates were performed from $K=i$ to $K=i$ (K=number of clusters). 
The best number of cluster (K) selected via the Integrated Completed Likelihood (ICL) criterion 
was `r FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$cluster.nb`.

```{r Coexp, message=FALSE, warning=FALSE, echo=FALSE, echo=FALSE, message=TRUE, warning=TRUE}

  out <- NULL
 
      out <- c(out, knitr::knit_child("CoExpAnal.Rmd", quiet=TRUE))  
    
knitr::asis_output(out)

```

`r  if(isFALSE(FlomicsMultiAssay@ExperimentList[[paste0(data,".filtred")]]@metadata[["CoExpAnal"]]$results)) {"\\end{comment}"}`
